---
title: "McDonald's Menu Report"
author: "Lujain Alghamdi"
date: "2022-10-06"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, message=FALSE}
# Set up
# download all necessary libraries
library(tidyr)
library(dplyr)
library(tidyverse)
library(GGally)
install.packages("janitor")
install.packages("here")
library(janitor)
library(here)
install.packages("reactable")
library(reactable)
# Get current working directory
getwd()
# Make sure the file we want to read from exists
file.exists("../data/menu.csv")
# Read the csv file and saved it in an object
menu <- read_csv("../data/menu.csv")
```

The dataset menu is a collection of calories, fat, and sugar for every cheeseburger, fries, and milkshake on the McDonald's menu. In this report we're gonna check the correlation between calories and other variables.

## Data

Following are the key variables in our data
```{r include=FALSE, message=FALSE}
# Show the structure of the dataset
glimpse(menu)
# Show the first 5 rows
head(menu)
# Check to see if there is any missing data
summary(menu)
# Since we have a lot of variables, This is a quick way to look at their names in a compact way
names(menu)
# Plot a subset of the data to see if there are any interesting relationships
ggpairs(menu, columns=c("Calories", "Sugars", "Saturated Fat (% Daily Value)"))
ggpairs(menu, columns=c("Calories","Cholesterol", "Total Fat (% Daily Value)"))
# Clean the variable names
menu %>%
  clean_names() -> menu
# Delete "serving size" cause it's not useful in our case
menu_withou_serv = select(menu, -3)
# Check names after deletion
names(menu_withou_serv)
# Gather the category and item variables together since they're not very distinct variables
menu_withou_serv %>%
  unite("Item",category, item, sep=" ") -> menu_withou_serv
# Check dimentions before tidying up the data
dim(menu_withou_serv)
# Use pivot_longer to tidy up the data
menu_withou_serv %>%
  pivot_longer(!Item, names_to= "Nutritional_Facts", values_to= "Values") -> menu_tidy
# Check dimentions after 
dim(menu_tidy)
```
```{r}
glimpse(menu_tidy)
reactable(menu_tidy)
```

## Explatory Data Analysis

Plotting a boxplot will help us catch any skewness and check the dispersion of the data. We can see that there aren't many outlers, but there exists a single extreme outlier in the Chicken & Fish category. 

```{r}
menu %>% 
  ggplot(aes(x= calories, y= category)) +
  geom_boxplot() 
```

After further investigation, we found that the item with the most calories is "Chicken McNuggets (40 piece)".
```{r}
#Lets try to find that max value
Max_Calories_ChickenFish <- menu$item[[which.max(menu$calories)]]
Max_Calories_ChickenFish
```
After checking sodium content and seeing if we can find any interesting insight. Once again we notice an extreme outlier in the data, which also turns out to be "Chicken McNuggets (40 piece)".
```{r}
menu %>% 
  ggplot(aes(x= category, y= sodium)) +
  geom_jitter()
Max_Sodium_ChickenFish <- menu$item[[which.max(menu$sodium)]]
Max_Sodium_ChickenFish
```
Calories and protein
```{r}
menu %>%
  group_by(category)%>%
  ggplot(aes(x=calories, y=protein))+
  geom_point()
```
Calories and cholesterol
```{r}
menu %>%
  group_by(category)%>%
  ggplot(aes(x=calories, y=cholesterol))+
  geom_point()
```
## Conclusion

